What We Eval in the Shadows

### 2021-04-17 paper/main.tex
Update 6.4

\Eval in R is mostly used for meta-programming purposes and to access
environments other than the local one. In Javascript, patterns are ad-hoc, such
as json loading and parsing, and can often be rewritten without \eval, such as
function or method call, or assignment to a local variable or an object
property. Compared to Javascript, \eval patterns in R we observed are much more
legitimate, although this is biased by the fact that our main corpus CRAN
features more experienced developers than websites found at large on the web.

\eval is a powerful tool and can be sometimes replaced with functions with more
specialized goals. For instance, variable lookup in any environment can be
performed with \c{get}, and assignment in any environment, with \c{assign}.
Building a call and executing can be done with \c{do.call}. Nevertheless, \eval
shines when expressions passed to it can be of many different types.

>>>>

\Eval in R is mostly used for meta-programming purposes and to access
environments other than the local one. In Javascript, patterns are ad-hoc, such
as json loading and parsing, and can often be rewritten without \eval, such as
function or method call, or assignment to a local variable or an object
property. For R, the data suggests that in some cases, the use of \eval in the
\c{X, V, \$, <-, FUN} and the function calls related to code generation could
replaced by more specific functions. For instance, variable lookup in any
environment can be performed with \c{get}, and assignment in any environment,
with \c{assign}. Building a call and executing can be done with \c{do.call}.
Nevertheless the many of the observed \eval usage in R, in particular the one
related to statistical modeling and DSLs are more sophisticated than those
reported for JavaScript.
